Efficient N-Dimensional surface estimation using Crofton formula and run-length encoding

### 2012-01-25 article/Article.tex
modifs mercredi 25/01

@@

% discretisation
The Crofton formula can be easily applied to discrete binary images \cite{Lang2001, Legland2007}. 
The integral over lines can be decomposed into an integral over a finite set of directions
and an integral over lines parallel to a given direction.
The number of connected components in the intersections of the structure with a discrete line
is obtained by counting the number of intercepts with its boundary.

@@

@@

\subsubsection{N-Dimensional name}
The attribute is called {\em Perimeter} independently of the dimension of the image and is available in the \verb$itk::ShapeLabelObject$.

\subsubsection{Border management}

@@

\subsubsection{Multithreading}

@@

\subsection{Circularity}

The (planar) circularity (often called "shape factor") is defined as:
\begin{eqnarray}
f = 4\pi \frac{A}{p^2}
\end{eqnarray}

Circularity takes values between $0$ and $1$. It is equal to $1$ for circular shapes, and decreases for elongated shapes.

[on garde la circularité ?]

@@

% % Example of reconstruction of a discrete disk
% \begin{figure}[!htb]
% \begin{center}
% \includegraphics[width=5cm]{discreteDisk.eps}
% %\includegraphics[width=5cm][bb=0 0 605 605]{chick.png}
% \end{center}
% \end{figure}

@@

>>>>

Dans l'intro, mettre :
* mesure perimetre ou surface est important
* liste des differentes methodes pour mesures surface / perimetre
    * choix marching cubes pour comparer
* parler des facteurs de forme et introduire "roundness"
* plan de l'article

@@

\subsection{Crofton formula in discrete images}

The Crofton formula can be easily applied to discrete binary images \cite{Lang2001, Legland2007}. 
The integral over lines can be decomposed into an integral over a finite set of directions
and an integral over lines parallel to a given direction.
The number of connected components in the intersections of the structure with a discrete line
is obtained by counting the number of intercepts with its boundary.

[Ajouter une formule avec des sommes a la place des integrales]

[dire comment on calcule les poids (1) des espaces entre les droites et (2) des poids associes aux directions]
[Cas des directions principales ($d$ en $nd$) et de toutes les directions (4 en 2D et 13 en 3D)]

@@

\subsection{Roundness}

The roundness is defined the ratio of equivalent $d$-perimeter over the measured $d$-perimeter:
\begin{eqnarray}
roundness = \frac{P_{eq}}{P}
\end{eqnarray}

Roundness takes values between $0$ and $1$. 
It is equal to $1$ for circular or spherical shapes, 
and decreases for more complicated shapes.

\section{Implementation}

@@

\subsection{N-Dimensional name}
The attribute is called {\em Perimeter} independently of the dimension of the image and is available in the \verb$itk::ShapeLabelObject$.

\subsection{Border management}

@@

\subsection{Multithreading}

@@

@@

 % Example of reconstruction of a discrete disk
\begin{figure}[!htb]
\begin{center}
\includegraphics[width=5cm]{images/discreteDisk}
\end{center}
\end{figure}

@@

Perimeter of 2D discretized shapes was measured using Crofton method using 2 and 4 directions, 
and by computing the length of the reconstructed contour (method ?).
Surface area of 3D discretized shapes was measured using Crofton method using 3 and 13 directions, 
and by computing the surface area of the reconstruced shape obtained by the marching cubes algorithm.
The average and the standard deviation of measurements were computed for all shapes discretized
with the same resolution. Effect of orientation was investigated by computing average and standard 
deviation of shapes having the same orientation.
